---
title: "p8105_hw3_lc3391"
author: "Lu Chen"
date: "10/13/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)

```

# Problem 1

## Importing dataset
```{r}
library(p8105.datasets)
data("instacart")

str(instacart)
```
### Short description of the dataset
- In the dataset instacart, there are 1384617 observations of  15 variables. It composes with both numeric and categorical data. Some key variables are 'aisle', 'reordered', 'product name' and so on. One example is that the Asian Chopped Salad with Dressing with product id 18394 located on aisle 123, Packaged Vegetables and Fruits, from department 4, Produce, is reordered once by customer with user id 182389. 

## Summarize the dataset
```{r}
instacart %>% 
  group_by(aisle) %>% 
  summarize(n_aisle=n()) %>% 
  arrange(desc(n_aisle))

#little comments: there are 134 aisles, and most intems are ordered from the aisle Fresh Vegetables.

instacart %>% 
  group_by(aisle) %>% 
  summarize(n_aisle=n()) %>% 
  filter(n_aisle > 10000) %>% 
  arrange(aisle) %>% 
  ggplot(aes(x = aisle, y = n_aisle)) +
  geom_point() +
  labs(
    title = "Items ordered in aisle",
    x = "Name of aisle",
    y = "Number of items ordered from the aisle",
    caption = "Data from the p8105 package"
  ) 

#Little comments: there are many aisles with more than 10000 items ordered, and the top 3 are: fresh veges, fresh fruits, and packaged vege and fruits.

instacart %>% 
  filter(aisle %in% c("baking ingredients", "dog food care", "packaged vegetables fruits")) %>% 
  group_by(aisle, product_name) %>% 
  summarize(sum_orders = sum(order_number)) %>% 
  mutate(order_rank = min_rank(desc(sum_orders))) %>%
  filter(order_rank %in% c(1,2,3)) %>%
  arrange(aisle, order_rank) %>% 
  knitr::kable()

#little comments: The three most popular items in baking ingredients aisle are Light Brown Sugar, Cane Sugar, and Organic Vanilla Extract; that in dog food care aisle are Standard Size Pet Waste Bags, Beef Stew Canned Dog Food, and Snack Sticks Chicken & Rice Recipe Dog Treats; that in packaged vegetables fruits aisle are Organic Baby Spainach, Organic Raspberries and Organic Blueberries.

instacart %>% 
  mutate(order_dow = recode(order_dow, "0" = "Sunday", "1" = "Monday", "2" = "Tuesday", "3" = "Wednesday", 
                            "4" = "Thursday", "5" = "Friday", "6" = "Saturday")) %>% 
  filter(product_name %in% c("Pink Lady Apples", "Coffee Ice Cream")) %>% 
  group_by(product_name, order_dow) %>% 
  summarize(mean_hour_of_day = mean(order_hour_of_day)) %>%
  pivot_wider(names_from = order_dow, values_from = mean_hour_of_day) %>% 
  knitr::kable()

#little comments: The mean order hour of the day for both products are concentrated on noon to afternoon (about 11:00 to 15:00).

```
## Problem 2

### Importing and cleaning the dataset
```{r}
library(p8105.datasets)
data("brfss_smart2010")

brfss_smart2010 = 
  brfss_smart2010 %>% 
  janitor::clean_names() %>% 
  filter(topic %in% c("Overall Health"), response %in% c("Excellent","Very good", "Good", "Fair", "Poor")) %>% 
  mutate(response = fct_relevel(response, "Poor","Fair","Good","Very good","Excellent"))

```

### Summarize the dataset
```{r}
brfss_smart2010 %>% 
  filter(year %in% c("2002")) %>% 
  group_by(locationabbr, locationdesc) %>% 
  summarize(n_loc = n()) %>% 
  group_by(locationabbr) %>% 
  summarize(n_loc = n()) %>% 
  filter(n_loc >= 7)

#little comments: 6 states were observed at 7 or more locations, and they are CT, FL, MA, NC, NJ, and PA.

brfss_smart2010 %>% 
  filter(year %in% c("2010")) %>% 
  group_by(locationabbr, locationdesc) %>% 
  summarize(n_loc = n()) %>% 
  group_by(locationabbr) %>% 
  summarize(n_loc = n()) %>% 
  filter(n_loc >= 7)

#little comments: there are 14 states were observed at 7 or more locations, and they are CA, CO, FL, MA, MD, NC, NE, NJ, NY, OH, PA, SC, TX, and WA.

brfss_smart2010 %>% 
  filter(response %in% c("Excellent")) %>% 
  group_by(year, locationabbr, locationdesc) %>% 
  summarize(average_data_value = mean(data_value)) %>%
  select(year, locationabbr, locationdesc, average_data_value) %>% 
  ggplot(aes(x = year, y = average_data_value)) +
  geom_line(aes(group = locationabbr)) +
  labs(
    title = "Spaghetti plot",
    x = "Year",
    y = "Average data value",
    caption = "Data from p8105 package"
  )
  
brfss_smart2010 %>% 
  filter(year %in% c("2006","2010"), 
         response %in% c("Excellent", "Very good", "Good", "Fair","Poor"), 
         locationabbr == "NY") %>% 
  ggplot(aes(x = response, y = data_value)) +
  geom_boxplot() +
  facet_grid(. ~ year) +
  labs(
    title = "Distribution of data value for year 2006 and 2010 in NY state",
    x = "Response",
    y = "data value",
    caption = "data from package p8105"
  )
  
```

## Problem 3

### reading in dataset and do the cleaning
```{r, warning=FALSE}
accel_data = read_csv("./data/accel_data.csv") %>% 
  janitor::clean_names() %>% 
  mutate(wkdays_wkends = case_when(
     day %in% c("Monday","Tuesday","Wednesday","Thursday","Friday") ~ "Weekday",
     day %in% c("Saturday","Sunday") ~ "Weekend"
  )) %>% 
  select(week, day_id, day, wkdays_wkends, everything())

str(accel_data)

# Comments: there are 35 observations of 1444 variables. Other than week, day_id, day, and weekday vs. weekend, the dataset contains activity counts for each minute of a 24-hour day starting at midnight.

accel_data %>% 
  mutate(tot_act_each = rowSums(select(.,activity_1:activity_1440))) %>%
  select(week, day_id, day, wkdays_wkends, tot_act_each) %>% 
  mutate(day_int = case_when(
     day == "Monday" ~ 1, day == "Tuesday" ~ 2, day == "Wednesday" ~ 3, day == "Thursday" ~ 4,
     day == "Friday" ~ 5, day == "Saturday" ~ 6, day == "Sunday" ~ 7
  )) %>% 
  arrange(week, day_int) %>% 
  select(week, day, tot_act_each) %>% 
  pivot_wider(names_from = week, values_from = tot_act_each) %>% 
  knitr::kable()

# comments: no apparent trends shown here

accel_data %>% 
  mutate(tot_act_each = rowSums(select(.,activity_1:activity_1440))) %>% 
  select(week, day_id, day, wkdays_wkends, tot_act_each) %>% 
  ggplot(aes(x = week, y = tot_act_each, color = day)) + 
  geom_point() +
  geom_smooth(size = 0.5, se = FALSE) +
  labs(
    title = "the 24-hour activity time courses for each day",
    x = "Week", 
    y = "Activity counts per day"
    ) 

# comments: the patient has a relatively unstable activity pattern for each day. It varies a lot from starting to ending point. On Monday and Saturday, the variation is greater than other days. And on Tuesday and Wednesday, the activity is quite stable.
```

