---
title: "p8105_hw3_lc3391"
author: "Lu Chen"
date: "10/13/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)

```

# Problem 1

## Importing daraset
```{r}
library(p8105.datasets)
data("instacart")

str(instacart)
```
### Short description of the dataset
- In the dataset instacart, there are 1384617 observations of  15 variables. It composes with both numeric and categorical data. Some key variables are 'aisle', 'reordered', 'product name' and so on. One example is that the Asian Chopped Salad with Dressing with product id 18394 located on aisle 123, Packaged Vegetables and Fruits, from department 4, Produce, is reordered once by customer with user id 182389. 

## Summarize the dataset
```{r}
instacart %>% 
  group_by(aisle) %>% 
  summarize(n_aisle=n()) %>% 
  arrange(desc(n_aisle))

#little comments: there are 134 aisles, and most intems are ordered from the aisle Fresh Vegetables.

instacart %>% 
  group_by(aisle) %>% 
  summarize(n_aisle=n()) %>% 
  filter(n_aisle > 10000) %>% 
  arrange(aisle) %>% 
  ggplot(aes(x = aisle, y = n_aisle)) +
  geom_point() +
  labs(
    title = "Items ordered in aisle",
    x = "Name of aisle",
    y = "Number of items ordered from the aisle",
    caption = "Data from the p8105 package"
  ) 

#Little comments: there are many aisles with more than 10000 items ordered, and the top 3 are: fresh veges, fresh fruits, and packaged vege and fruits.

instacart %>% 
  filter(aisle %in% c("baking ingredients", "dog food care", "packaged vegetables fruits")) %>% 
  group_by(aisle, product_name) %>% 
  summarize(sum_orders = sum(order_number)) %>% 
  mutate(order_rank = min_rank(desc(sum_orders))) %>%
  filter(order_rank %in% c(1,2,3)) %>%
  arrange(aisle, order_rank) %>% 
  knitr::kable()

#little comments: The three most popular items in baking ingredients aisle are Light Brown Sugar, Cane Sugar, and Organic Vanilla Extract; that in dog food care aisle are Standard Size Pet Waste Bags, Beef Stew Canned Dog Food, and Snack Sticks Chicken & Rice Recipe Dog Treats; that in packaged vegetables fruits aisle are Organic Baby Spainach, Organic Raspberries and Organic Blueberries.
```


